Kindly Bent to Free Us

### 2020-06-30 kindly/main.tex
Add a section with some potential extensions.
Pre-submit fixes.
first round of revision
Fixed compilation error '\Bbbk already defined'.
Expand the comparison table.
acknowledgments
Prepare for camery ready.

\PassOptionsToPackage{svgnames}{xcolor}
\documentclass[acmsmall,review,anonymous]{acmart}
\settopmatter{printfolios=true,printccs=false,printacmref=false}

@@

% Math
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{thm-restate}
% \usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{textcomp}
\usepackage{gensymb}
% \usepackage{textgreek}
\usepackage{multicol}

@@

\usepackage{caption}
\usepackage{subcaption}
\usepackage[inline,shortlabels]{enumitem}
\setlist{leftmargin=*,noitemsep}
\usepackage{array}
\usepackage{bm}%Decent bolding for math symbols

@@

\bibliographystyle{ACM-Reference-Format}

\author{Gabriel Radanne}
\affiliation{
  \institution{University of Freiburg}
  \country{Germany}
}
\email{radanne@informatik.uni-freiburg.de}

@@

\input{intro}
\input{motivation}
\input{lang}
\input{infer/infer}
\input{metatheory}
\input{soa}
\input{conclusion}

@@

\section{Further Examples}
\label{sec:extra-example}
\lstMakeShortInline[keepspaces,basicstyle=\small\ttfamily]@
\input{motivation-linearity}
\input{motivation-pool}
\lstDeleteShortInline@

>>>>

\PassOptionsToPackage{svgnames}{xcolor}
\documentclass[acmsmall,screen]{acmart}

% The page limit for final papers is 27 pages, not including references (but 
% including appendices). Additional materials may be uploaded to ACM's 
% Digital Library, in a manner that the publisher will clarify in 
% instructions sent to you separately. In extraordinary circumstances, I'm 
% able to grant further pages still, and please write to me if you think your 
% paper might qualify. There's no fee associated with the number of pages 
% you use, but we do want to be fair to all authors in allocating space.

@@

% Math
\usepackage{amsmath}
\usepackage{amsfonts}
% \usepackage{amssymb}
\usepackage{amsthm}
\usepackage{thm-restate}
% \usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{textcomp}
\usepackage{gensymb}
% \usepackage{textgreek}
\usepackage{multicol}

@@

\usepackage{caption}
\usepackage{subcaption}
\usepackage[inline,shortlabels]{enumitem}
\setlist{leftmargin=*,noitemsep}
\usepackage{array}
\usepackage{adjustbox}
\usepackage{bm}%Decent bolding for math symbols
\usepackage{pifont}%% check mark

@@

\bibliographystyle{ACM-Reference-Format}
\citestyle{acmauthoryear}

%%% The following is specific to ICFP '20 and the paper
%%% 'Kindly Bent to Free Us'
%%% by Gabriel Radanne, Hannes Saffrich, and Peter Thiemann.
%%%
\copyrightyear{2020}
\acmSubmissionID{icfp20main-p74-p}
\setcopyright{rightsretained}
\acmJournal{PACMPL}
\acmYear{2020} \acmVolume{4} \acmNumber{ICFP} \acmArticle{103} \acmMonth{8} \acmPrice{}\acmDOI{10.1145/3408985}

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10011007.10011006.10011039.10011311</concept_id>
       <concept_desc>Software and its engineering~Semantics</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10011007.10011006.10011008.10011009.10011012</concept_id>
       <concept_desc>Software and its engineering~Functional languages</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10011007.10011006.10011008.10011009.10011010</concept_id>
       <concept_desc>Software and its engineering~Imperative languages</concept_desc>
       <concept_significance>300</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Semantics}
\ccsdesc[500]{Software and its engineering~Functional languages}
\ccsdesc[300]{Software and its engineering~Imperative languages}

\author{Gabriel Radanne}
\affiliation{
  \institution{Inria}
  \country{Paris}
}
\email{gabriel.radanne@inria.fr}

@@

\input{intro}
\input{motivation}
\input{lang}
\input{infer/infer}
\input{metatheory}
\input{extensions}
\input{soa}
\input{conclusion}

\begin{acks}
  This material is based upon work supported by the German Research
  Council, \grantsponsor{sponsor01}{DFG}{https://www.dfg.de/}, project reference number
  \grantnum{sponsor01}{TH 665/11-1}. We are indebted to the anonymous reviewers
  for their thoughtful and constructive comments.
\end{acks}

@@

\section{Further examples}
\label{sec:extra-example}
\lstMakeShortInline[keepspaces,basicstyle=\small\ttfamily]@
\input{motivation-linearity}
\input{motivation-pool}
\lstDeleteShortInline@
